% EXAMPLE base CV for Jordan Doe — replace with your own.
% Self-contained: compiles with plain `pdflatex cv.tex`, no custom class.
% The tailoring agent COPIES this file and reshapes the copy per each job;
% it never edits this base. Keep it to one page.
\documentclass[10pt,letterpaper]{article}
\usepackage[margin=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}

\setlist[itemize]{leftmargin=1.2em, topsep=1pt, itemsep=1pt, parsep=0pt}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{6pt}{3pt}
\pagestyle{empty}

\begin{document}

\begin{center}
  {\LARGE\bfseries Jordan Doe}\\[2pt]
  jordan.doe@example.com $\cdot$ (555) 010-0000 $\cdot$ Remote (US), open to relocation\\
  github.com/jordandoe $\cdot$ linkedin.com/in/jordandoe
\end{center}

\section*{Summary}
Software engineer with ~5 years building and shipping machine-learning systems,
from data pipelines to on-device inference. Owns features end-to-end and works
directly with the people who use them.

\section*{Experience}
\textbf{Senior Software Engineer}, Example Analytics Inc. \hfill 2022--present
\begin{itemize}
  \item Led a 3-person team building an internal LLM assistant that answers support questions from product docs, cutting average ticket handling time.
  \item Built the retrieval and evaluation harness (embeddings, reranking, offline evals) and owned deployment behind a FastAPI service.
  \item Partnered with two enterprise customers to deploy the assistant in their environments, iterating on real usage.
\end{itemize}

\textbf{Machine Learning Engineer}, Sample Robotics Co. \hfill 2020--2022
\begin{itemize}
  \item Trained and quantized vision models for an embedded perception stack; shipped an int8 model within the device's latency budget.
  \item Wrote data tooling and a benchmarking rig used across the perception team.
\end{itemize}

\section*{Projects}
\begin{itemize}
  \item \textbf{Open-source inference toolkit} --- a small library for running quantized transformer models on CPU; a few hundred GitHub stars.
\end{itemize}

\section*{Skills}
Python, C++, TypeScript $\cdot$ PyTorch, ONNX, quantization (PTQ/QAT), RAG, evals $\cdot$ FastAPI, Docker, SQLite/Postgres, Linux

\section*{Education}
M.S. \& B.S. Computer Science, Example State University \hfill 2018, 2020

\end{document}
